\fancyhead[C]{Section 13.3}
\fancyhead[R]{\dayfive}

\section*{\centering Chapter 13.3: The Arc Length Formula}

\textbf{G3: Geometry of Curves.} I can compute the arc length of a curve in two or three dimensions and apply arc length to solve problems. I can compute normal vectors and curvature for curves in two and three dimensions.  I can interpret these objects geometrically and in applications.

\subsection*{Mechanics}
\begin{enumerate}
    \item \question{Find the length of the curve 
	\[
	\br(t) = \langle\sqrt{2}t,\sqrt{3}t,(1-t)\rangle
	\]
	from $(0,0,1)$ to $(\sqrt{2}, \sqrt{3}, 0)$}
    {% answer goes here

    }
    {% solution goes here
    } 
    \item \question{Let $\br(t)=\langle 6 \sin 2t, 6 \cos 2t, 5t\rangle $. Find the unit tangent vector of $\br(t)$ and find the length of the portion of the graph of $\br(t)$ where $0 \leq t \leq \pi$.}
    {% answer goes here

    }
    {% solution goes here
    } 
    \item \question{Suppose an object's position is given by $\br(t)= (2\ln (t+1))\bi+(e^{2t}+t)\bj+(\sin^2(t))\bk$. Set up but do not evaluate the appropriate integral with limits to find the distance the object traveled from the point $A(0,1,0)$ to the point $B(\ln 4,e^2+1,\sin^2(1))$.}
    {% answer goes here

    }
    {% solution goes here
    } 
    \item \question{Suppose you are standing at the point $(0,0,5)$ and walk 13 units along the path $(5\sin t, 12t, $ $5\cos t)$ in the direction of increasing $t$. Where do you end up?}
    {% answer goes here

    }
    {% solution goes here
    } 
	
\end{enumerate}
\subsection*{Applications}
\begin{enumerate}[resume]
    \item \question{A DNA molecule has the structure of a double helix (ie., two intertwined helices). Its radius is about 1 nanometre, and each loop of the helix rises about 3.4 nanometres. Supposing that a full molecule consists of $2.9 \times 10^8$ loops, compute the approximate length of a molecule of DNA. }
    {% answer goes here

    }
    {Helices always have the form $\br(t) = (\cos t, \sin t, t)$, for $t\in [0,2\pi]$, however to fit this helix to our specifications, we need to involve some transformation factors. With units in nanometres (nm), the radius being unital implies there is no scaling term on the cosine and sine. Since the helix needs to rise 3.4 nm, the $z$-coordinate needs to be $t\mapsto \frac{3.4}{2\pi}t$. Since a strand of DNA consists of two identical interlaced helices, we have that, and a molecule of DNA is $2.8 \times 10^8$ copies of this loop, we have that 
\begin{align*}
\textrm{Length of DNA } &= 2\times 2.8\times 10^8 \times \int_0^{2\pi}\|\br'(t)\|dt \\
&= 2\times 2.8\times 10^8 \times \int_0^{2\pi}\sqrt{1+\left(\frac{3.4}{2\pi}\right)^2}dt \\ 
&=2 \times 2.8\times 10^8 \times 2\pi\sqrt{1+\left(\frac{3.4}{2\pi}\right)^2}\\
&\approx 4\times 10^9 \textrm{ nm} = 4 \textrm{ m}
\end{align*}
We remark that the typical cited length of a molecule of DNA being 2 metres long comes from identifying the DNA as a double helix. Here, we've unraveled the double strands, hence why the length increased twofold. 
    } 
\end{enumerate}
\subsection*{Extensions}
\begin{enumerate}[resume]

	
	\item \question{Find the point on the curve
	\[
	\br(t) = (5 \sin t)\bi+(5 \cos t)\bj+12t\bk
	\]
	at a distance $26\pi$ units along the curve from the point $(0,5,0)$ in the direction of increasing arc length.}
    {% answer goes here

    }
    {% solution goes here
    } 
    \item \question{This problem is meant to generalize the previous one. Let $\br(t)$ be a smooth curve defined for $t\geq 0$. Suppose further that $|\br'(t)|\geq 0.01$ for all $t$. Show that if you are given a positive number $D$, you can find a (unique!) corresponding point $P$ on the curve, so that the distance from $\br(0)$ to $P$ along the curve equals $D$. Also, show that if we just assumed that $|\br'(t)| >0$ for all $t$, this statement is no longer true.}
    {% answer goes here

    }
    {% solution goes here
    } 

	
	.
\end{enumerate}
{}

\iftoggle{answers}{\begin{center}{\large \textbf{Math 2551 Worksheet Answers: Arc Length}}
\end{center}

\begin{enumerate}	


\item $\bT(t)=\dfrac{1}{13}\langle 12\cos(2t),-12\sin(2t),5\rangle $

length: $13\pi$


\item $(0,5,24\pi)$

\item $\Ds \int_0^1 \sqrt{(\dfrac{2}{t+1})^2+(2e^{2t}+1)^2+(2\sin(t)\cos(t))^2}\ dt$

\item $\sqrt{6}$

\end{enumerate}
}{}
\iftoggle{solutions}
{
Solutions go here in the same format.
}{}
