\fancyhead[C]{Section 14.6}
\fancyhead[R]{\daytwelve}

\section*{\centering Chapter 14.6: Linearization and Tangent Planes}

\textbf{D2: Tangent Planes and Linear Approximations.} I can find equations for tangent planes to surfaces and linear approximations of functions at a given point and apply these to solve problems.

\subsection*{Mechanics}
\begin{enumerate}	
    \item %14.6 # 30b
    \question{Find the linearization of $f(x,y)=e^{2y-x}$ at $(1,2)$. Without doing any more calculations, find an equation of the tangent plane of the surface $f(x,y)$ at $(1,2)$.}
    {% answer goes here
    $L(x,y)=e^3-e^3(x-1)+2e^3(y-2)$
    
    tangent plane: $z=e^3-e^3(x-1)+2e^3(y-2)$
    }
    {% solution goes here
    }
     
	
	\item \question{Find the linearization of $f(x,y,z)=\arctan(xyz)$ at $(1,1,0)$.}
    {% answer goes here
    $L(x,y,z)=z$
    }
    {% solution goes here
    } 
	\item \question{Use the linearization to approximate $f(2.95, 7.1)$ for the function $f(x,y)=\sqrt{x^2+y}$, knowing that $f(3,7)=4$.	}
    {% answer goes here
    $f(2.95, 7.1)\approx 4-1/40$
    }
    {We are given a surface defined by $z = f(x,y)$. Recall that we can obtain a normal vector by defining the auxiliary function $g(x,y,z) = f(x,y)-z$ and taking the level set $g(x,y,z) = 0$. We would obtain that $\nabla g = (f_x,f_y, -1)$. Given $f(x,y) = \sqrt{x^2+y}$, we've got that 
\begin{equation*}
    \bn = \left.\left(\frac{x}{\sqrt{x^2+y}},\frac{1}{2\sqrt{x^2+y}},-1\right)\right|_{(3,7)} = \left(\frac{3}{4},\frac{1}{8},-1\right)
\end{equation*}
and thus an equation of the tangent plane is 
\begin{equation*}
   \frac{3}{4}(x-3)+\frac{1}{8}(y-7)-(z-4)=0
\end{equation*}
\subsection*{3}
We will need to know the normal vector to the tangent plane to understand the reflection angle. Luckily for us, we know that one possible normal vector should just be $\nabla f$, where $f(x,y,z) =x^2+y^2-z$. Thus, $\bn = (2x,2y,-1)$, evaluated at the point $(1,1,2)$ so $\bn = (2,2,-1)$. We also only need the angle of incidence because the law of reflection states it is identical to the angle of reflection. Note that as written, the ray of light points \textit{towards} the paraboloid. So in order to get the correct angle, we need the arrows to point \textit{outwards} from the paraboloid. Therefore the expression we should evaluate is 
\begin{equation*}
    \theta_r = \arccos \frac{\bn \cdot (2,3,-2)}{\|\bn\|\times \|(2,3,-2)\| }=\arccos \frac{12}{3\sqrt{17}} \approx 0.25
\end{equation*}
    }
    \item \question{Find an equation of the tangent plane to the unit sphere $x^2+y^2+z^2=1$ at the point $\left(\dfrac{1}{\sqrt{2}},\dfrac{1}{2},\dfrac{1}{2}\right)$.}
    {% answer goes here
        $\sqrt{2}\left( x-\dfrac{1}{\sqrt{2}}\right)+\left(y-\dfrac{1}{2}\right)+\left(z-\dfrac{1}{2}\right)=0$
    }
    {When a surface is expressed as the level set of a 3-variable function, the normal vector to any tangent plane is just the gradient. So for us, it will be $\nabla f = (2x,2y,2z)$ where $f(x,y,z)=x^2+y^2+z^2$. Therefore, 
\begin{equation*}
    \bn = (2x,2y,2z)|_{\left(\frac{1}{\sqrt 2},\frac{1}{ 2},\frac{1}{ 2}\right)} = \left(\sqrt{2},1,1\right)
\end{equation*}
and so an equation of the tangent plane is
\begin{equation*}
    \sqrt 2\left(x-\frac{1}{\sqrt 2}\right)+\left(y-\frac{1}{ 2}\right)+\left(z-\frac{1}{ 2}\right)=0
\end{equation*}
}
\end{enumerate} 
\subsection*{Applications}
\begin{enumerate}[resume]
    \item \question{Suppose you are shining a flashlight on a smooth surface. The \emph{angle of incidence}, $\theta_i$ is the angle at which a light beam hits the surface, measured with respect to the surface normal (i.e., the normal vector to the tangent plane at point of contact). 
    The \emph{angle of reflection} $\theta_r$ is the angle of the reflected light beam measured with respect to the surface normal. 
    The \emph{law of reflection} states that in a vacuum, we must have $\theta_i=\theta_r$. 
    Draw a labeled picture to convince yourself that this is reasonable.
    
    Now, consider the paraboloid $z = x^2+y^2$, and a light ray traveling along the path $\mathbf{r}(t)= (-2,-3,2)t+(3,4,0)$. 
    Compute the angle of reflection at the point $(1,1,2)$ 
    [\emph{Hint: How can one find the angle between two vectors?}]. }
    {% answer goes here
     $\theta_r = \arccos(\frac{4}{\sqrt{17}})\approx 0.245\ \text{rad}$
    }
    {We will need to know the normal vector to the tangent plane to understand the reflection angle. Luckily for us, we know that one possible normal vector should just be $\nabla f$, where $f(x,y,z) =x^2+y^2-z$. Thus, $\bn = (2x,2y,-1)$, evaluated at the point $(1,1,2)$ so $\bn = (2,2,-1)$. We also only need the angle of incidence because the law of reflection states it is identical to the angle of reflection. Note that as written, the ray of light points \textit{towards} the paraboloid. So in order to get the correct angle, we need the arrows to point \textit{outwards} from the paraboloid. Therefore the expression we should evaluate is 
\begin{equation*}
    \theta_r = \arccos \frac{\bn \cdot (2,3,-2)}{\|\bn\|\times \|(2,3,-2)\| }=\arccos \frac{12}{3\sqrt{17}} \approx 0.25
\end{equation*}
    } 
\end{enumerate}
\subsection*{Extensions}
\begin{enumerate}[resume]	
    \item \question{Use software to graph the function $z=x^{1/3}y^{1/3}$.  
    Examine the graph at $(0,0)$ - does it look like the function has a tangent plane there? 
    Use this to deduce a necessary condition for a function $f(x,y)$ to have a tangent plane. }
    {% answer goes here
    No, there are two different tangent planes.  The function cannot have a cusp at the point with the tangent plane.
    }
    {% solution goes here
    } 
\end{enumerate}