\fancyhead[C]{Section 15.7}
	\fancyhead[R]{\daynineteen}
	
\iftoggle{questions}{
\begin{center}{\large \textbf{Math 2551 Worksheet: Triple Integrals in Cylindrical \& Spherical Coordinates}}
\end{center}

During studio, do the set up portion of these integrals only.  You can practice doing the evaluation after studio.  Both the correct triple integral and correct final answer are given in the answers for this worksheet.

\begin{enumerate}
	
	\item Convert the integral $\displaystyle \int_{-1}^1 \int_0^{\sqrt{1-y^2}} \int_0^x (x^2+y^2) \ dz \ dx \ dy$ into an integral in cylindrical coordinates, and evaluate the integral.
	
	\item Suppose $a \geq 0$. Find the volume of the region cut from the solid sphere $\rho \leq a$ by the half-planes $\theta=0$ and $\theta= \pi/6$ in the first octant.
	
	\item Find the volume of the solid that lies within the sphere $x^2+y^2+z^2=4$, above the $xy$-plane, and below the cone $z=\sqrt{x^2+y^2}$.
	
	\item Find the volume of the region bounded above by the paraboloid $z=9-x^2-y^2$, below by the $xy$-plane, and lying \emph{outside} the cylinder $x^2+y^2=1$.
	
	\item Find the volume of the solid that is between the spheres $\rho=\sqrt{2}$ and $\rho=2$, but outside of the circular cylinder $x^2+y^2=1$.  It will be helpful to draw a cross-section in a plane $\theta=c$ for this problem and to use symmetry.
	
	\item Let $D$ be the right circular cylinder whose base is the circle $r=2\sin \theta$ in the $xy$-plane and whose top lies in plane $z=4-y$. Recall that $r=2 \sin \theta$ describes a circle centered at $(0,1)$ with radius $1$ in the $xy$-plane. Using cylindrical coordinates,
	\begin{enumerate}
		\item find the volume of the region $D$.
		\item find the $\bar{x}$ component of the centroid of the region (hint: use symmetry).
	\end{enumerate}
\end{enumerate}
}{}

\iftoggle{answers}{
\begin{center}{\large \textbf{Math 2551 Worksheet Answers: Triple Integrals in Cylindrical \& Spherical Coordinates}}
\end{center}

\begin{enumerate}
	\item Integral: $\Ds \int_{-\pi/2}^{\pi/2} \int_0^1 \int_0^{r\cos(\theta)}r^3\ dz\ dr\ d\theta$
	
	Answer: $\dfrac{2}{5}.$
	
	\item Integral: $\Ds \int_0^{\pi/6} \int_0^{\pi/2} \int_0^a \rho^2\sin(\phi)\ d\rho\ d\phi\ d\theta$
	
	Answer: $\dfrac{a^3\pi}{18}.$
	
	\item Integral: $\Ds \int_0^{2\pi} \int_{\pi/4}^{\pi/2} \int_0^2 \rho^2\sin(\phi)\ d\rho\ d\phi\ d\theta$ 
	
	Answer: $\dfrac{8\sqrt{2}\pi}{3}$
	
	\item Integral: $\Ds \int_0^{2\pi} \int_1^3 \int_0^{9-r^2} r\ dz\ dr\ d\theta$
	
	Answer: $32\pi$
	
	\item Integral: $\Ds 2 \left( \int_0^{2\pi}\int_{\pi/6}^{\pi/4} \int_{\csc(\phi)}^{2} \rho^2\sin(\phi)\ d\rho\ d\phi\ d\theta +\int_0^{2\pi}\int_{\pi/4}^{\pi/2} \int_{\sqrt{2}}^{2} \rho^2\sin(\phi)\ d\rho\ d\phi\ d\theta \right)$
	
	Answer: $\dfrac{12\sqrt{3}-4}{3}\pi $.
	
	\item \begin{enumerate}
		\item Integral: $\Ds \int_0^{\pi} \int_0^{2\sin(\theta)} \int_0^{4-r\sin(\theta)} r\ dz\ dr\ d\theta$
		
		Answer: $3\pi.$
		\item $\bar{x}=0$.
	\end{enumerate}
\end{enumerate}

}{}
\iftoggle{solutions}
{
Solutions go here in the same format.
}{}
