
\fancyhead[C]{Section 15.8}
\fancyhead[R]{\daytwenty}

\section*{\centering Chapter 15.8: The Change of Variables Formula}

\subsection*{Mechanics}
\begin{enumerate}
    	
	\item \question{Find the Jacobian determinant of the transformation $x=e^{-r}\sin(\theta), y=e^r\cos(\theta)$.}
        {% answer here
        
        }
        {% solution here
        
        }
        \item An ellipse in the plane has the equation $\left(\dfrac{x}{a}\right)^2+\left(\dfrac{y}{b}\right)^2=1$ for positive numbers $a$ and $b$. Use a change of variables to compute the area of this ellipse. \textit{[Note: Without a change of variables, you would likely need a trig substitution to do this!]}
        {% answer here
        
        }
        {% solution here
        
        }
        \item \question{Compute $ \iint_R e^{x+y}\ dA$, where $R$ is the region given by the inequality $|x|+|y|\leq 1$. \textit{[Hint: Sketching the region should reveal a natural choice of transformation to use.]}}
        {% answer here
        
        }
        {% solution here
        
        }
        \item \question{Use the change-of-variables formula to justify the cylindrical and spherical volume elements $dx \ dy \ dz = rdr\ d\theta \ dz = \rho^2\sin \varphi \ d\rho \ d\theta \ d\varphi$ we learned last week.}
        {% answer here
        
        }
        {% solution here
        
        }
        \item \question{Solve the system \[u=2x-3y, v=-x+y \] for $x$ and $y$ in terms of $u$ and $v$.  Then find the value of the Jacobian and find the image of the parallelogram $R$ in the $xy$-plane with boundaries $x=-3, x=0, y=x,$ and $y=x+1$ under this transformation.  Sketch the transformed region in the $uv$-plane.  Use your results to rewrite the integral \[\iint_R 2(x-y)\ dx\ dy \] as an integral in $uv$-coordinates.}
        {% answer here
        
        }
        {% solution here
        
        }
\end{enumerate}

\subsection*{Extensions}
\begin{enumerate}[resume]

	\item \question{ Find equations for a transformation $\bT$ that maps a rectangular region $S$ in the $uv$-plane whose sides are parallel to the $u$- and $v$-axes onto the region $R$ bounded by the hyperbolas $y=1/x, y=3/x$ and the lines $y=x, y=3x$ in the first quadrant.}
        {% answer here
        
        }
        {% solution here
        
        }
    \item \question{ Use a change of variables to compute \[ \iint_R xy\ dA, \] where $R$ is the region in the first quadrant bounded by the lines $y=x$ and $y=3x$ and the hyperbolas $xy=1, xy=3$. \textit{[Hint: Consider the above problem.]}}
        {% answer here
        
        }
        {% solution here
        
        }
\end{enumerate}
{}

\iftoggle{answers}
{
	\begin{center}{\large \textbf{Math 2551 Worksheet Answers: Change of Variables}}
	\end{center}

	\begin{enumerate}
		\item $\sin^2(\theta)-\cos^2(\theta)=-\cos(2\theta)$
		
		\item The elliptical region $\dfrac{x^2}{a^2}+\dfrac{y^2}{b^2}\leq 1$.\\
		
		Many possible answers: any such should involve an integration problem where the region of integration is an ellipse with major and minor axes parallel to the $x$ and $y$-axes.
		
		\item $x=\sqrt{\dfrac{u}{v}}, y=\sqrt{uv}$ maps $[1,3]\times[1,3]$ onto $R$	
		
		\item  $\displaystyle\int_0^1 \int_{-3v}^{-3v+3} -2v \ du\ dv $
		
		\item $\ln(9)$
		
		\item $e+\dfrac{1}{e}$
	\end{enumerate}
}{}
\iftoggle{solutions}
{
Solutions go here in the same format.
}{}
