
\fancyhead[C]{Section 14.1}
\fancyhead[R]{\dayseven}

\section*{\centering Chapter 14.1: Multivariate Functions}

\textbf{G4: Surfaces.} I can identify standard quadric surfaces including: spheres, ellipsoids, elliptic paraboloids, hyperboloids, cones, and hyperbolic paraboloids. I can match graphs of functions of two variables to their equations and contour plots and determine their domains and ranges.

\vspace{-.5cm}
\subsection*{Mechanics}
\begin{enumerate}	
	\item \question{Algebraically describe the domains of each of the following functions. Then sketch them on (separate) $xy$-planes. 
	\begin{enumerate}
		\item $f(x,y)=\sqrt{x-y-1}.$
		
		\item $f(x,y) = \sqrt{(x-4)(y^2-1)}.$
		
		\item $f(x,y)=\cos^{-1}(y-4x^2)$.
		
		\item $f(x,y)= \dfrac{1}{4-x^2-y^2}.$
		
		\item $f(x,y)=\dfrac{1}{\ln(4-x^2-y^2)}$
	\end{enumerate}}
	{%answer
	\begin{enumerate}
		\item $\{ (x,y)\mid x-y\geq 1 \}$
		
		\item $\{ (x,y) \mid x\geq 4, |y|\geq 1 \} \cup \{(x,y) \mid x<4, |y|<1 \}$
		
		\item $\{ (x,y) \mid 4x^2-1\leq y\leq 4x^2+1 \}$
		
		\item All of $\R^2$ except the circle $x^2+y^2=4$
		
		\item All of the disk $x^2+y^2< 4$ except the circle $x^2+y^2=3$.
	\end{enumerate}
	}{ %solution

	}
	
	\item \question{For each of the surfaces (a)-(g), determine if the proposed descriptions of the level curves are correct. If not, give a correct descriptor. \textit{[Note: consider a point as a circle/ellipse of radius 0]}
		\begin{enumerate}
			\item $z=2x^2-3y^2$; Level curves are concentric ellipses. 
			\item $z=x^2+y^2$; Level curves are concentric circles
			\item $z=\dfrac{1}{x+y}$; Level curves are lines, whenever $x \neq -y$. 
			\item $z=2x+3y$; Level curves are parallel planes. 
			\item $z=\sqrt{25-x^2-y^2}$; Level curves are concentric circles, but only if $z> 5$ or $z<-5$
			\item $z=\sqrt{x^2+y^2}$; Level curves are concentric circles, but only if $z\geq 0$. 
			\item $z=xy$; Level curves are hyperbolas.
		\end{enumerate}
		}
		{%answer
			\begin{enumerate}
				\item Not correct; level curves are hyperbolas
				\item Correct
				\item Correct
				\item Not correct; level curves are parallel lines
				\item Not correct; level curves are concentric circles, but only if $0\leq z \leq 5$.
				\item Correct
				\item Correct
			\end{enumerate}
		}
		{%solution
		}
\end{enumerate}

\vspace{-.5cm}
\subsection*{Applications}
\begin{enumerate}[resume]
    \item \question{Multivariable functions are often used in economic models to describe how one should price an asset, or how to determine the utility of a product. For example, consider a \textit{utility function} $u(x,y,z)$, where $x,y,z$ represent three independent properties of an object (eg., price, quantity, quality), and $u$ tells you how much you value that item. In this context, what economic significance do the level surfaces $u(x,y,z) = C$ have (assume $C$ is a constant)? Give a example of how this phenomenon might manifest in your day-to-day life. 
	}{%answer
	The level surfaces tell you all combinations of price, quantity, and quality that you value the amount $C$.
	}
	{%solution
	}
\end{enumerate}

\vspace{-.5cm}
\subsection*{Extensions}
\begin{enumerate}[resume]
    \item \question{Find an equation for the level surface of the function $f(x,y,z)=\sqrt{x^2+y^2+z^2}$ passing through $(1,1,1)$. Sketch a plot of this level surface in $\mathbb{R}^3$.
	}
	{%answer
	The sphere $3=x^2+y^2+z^2$
	}
	{%solution
	
	}
    
    \item \question{Let $f(x,y) = (x-y)^2$. Determine the equations and shapes of the cross-sections when $x = 0$, $y = 0$, and $x = y,$ and describe the level curves. Use this information to produce a sketch of the graph of the surface.  Confirm your sketch using a 3d graphing utility.
	}
	{When $x=0$, the cross-section is the parabola $z=y^2$. 
	
	When $y=0$, the cross-section is the parabola $z=x^2$.
	
	When $x=y$, the cross-section is the line $z=0$.
	
	The level curves are pairs of parallel lines $y=x\pm\sqrt{k}$.
	}
	{%solution
	}
\end{enumerate}
