\fancyhead[C]{Section 12.1}
\fancyhead[R]{\daytwo}

\section*{\centering Chapter 12.1: Geometry in 3 Dimensions}

\subsection*{Mechanics}
\begin{enumerate}
	\item \question{Find the components of the vector	in 3-space of length 3 lying in the $yz$-plane pointing upward at an angle of $\pi/6$ measured from the positive $y$-axis.}{$x=0, y= 3\sqrt{3}/2, z=3/2$.}
    {%Solution here
    }
    \item \question{Describe in words, and with a sketch, the region of $\R^3$ given by the following equations or inequalities.
    \begin{enumerate}
        \item $y=x^2$
        \item $z=y$
        \item $0\leq z\leq 5$
        \item $0\leq z\leq 5$, $1\leq y \leq 6$
        \item $0\leq z\leq 5$, $1\leq y \leq 6$, $-2\leq x \leq 3$
    \end{enumerate}}{% answer goes here
    }
    {% solution goes here
    }
\end{enumerate}

\subsection*{Applications}

    \begin{enumerate}[resume]

	\item \question{Which is traveling faster, a car whose velocity vector is $\langle 28,33 \rangle$ km/h or a car whose velocity vector is $\langle 40, 0 \rangle$ km/h?  At what speed is the faster car traveling?}
    {% answer goes here
    }
    {% solution goes here
    }
    \item \question{A pilot is steering a plane in the direction N$45^\circ$W at an airspeed of 180 mph. A wind is blowing in
the direction S$30^\circ$E at a speed of 35 mph. Find the true course and the ground speed of the plane.}
    {% answer goes here
    }
    {% solution goes here
    }
\item \question{Three forces act on an object. One of the force vectors is $(25,0,0)$ Newtons. The second lies on the $xy$-plane at an angle of $60^\circ$ measured anticlockwise from the $x$-axis at a magnitude of 12N. The third is perpendicular to the plane of these two
forces and has magnitude 4N. Calculate the magnitude of a fourth force that would exactly counterbalance these three forces.}{% answer goes here
    }
    {% solution goes here
    }
\end{enumerate}

\subsection*{Extensions}
\begin{enumerate}[resume]
\item \question{Find the equation of a sphere of radius $4$ in $\R^3$ centered at the point $(1,-2,3)$.}
    {% answer goes here
    }
    {% solution goes here
    }
    \item \question{Find the equation of a ellipsoid centered at the origin, passing through the points $(5,0,0)$, $(0,\frac{1}{4}, 0)$ and $(0,0,3)$}
    {% answer goes here
    }
    {% solution goes here
    }
    \item \question{Use vectors to prove that the line joining the midpoints of
two sides of a triangle is parallel to the third side and half
its length.}{% answer goes here
    }
    {% solution goes here
    }
    \end{enumerate}
{}

\iftoggle{answers}{\begin{center}{\large \textbf{Math 2551 Worksheet Answers: $\R^3$}}
\end{center}


\begin{enumerate}
	\item $x=0, y= 3\sqrt{3}/2, z=3/2$.
	
	\item The first car is faster, at approx 43.28 km/h.
	
	\item $(x-1)^2+(y+2)^2+(z-3)^2=16$.
\end{enumerate}
}{}
\iftoggle{solutions}
{
Solutions go here in the same format.
}{}
