
\fancyhead[C]{Section 15.2}
\fancyhead[R]{\dayfifteen}

\section*{\centering Chapter 15.2: General Double Integrals}
\textbf{I1: Double \& Triple Integrals.} I can set up double and triple integrals as iterated integrals over any region. I can sketch regions based on a given iterated integral.\\\\
\textbf{I2: Iterated Integrals.} I can compute iterated integrals of two and three variable functions, including applying Fubini's Theorem to change the order of integration of an iterated integral.

\subsection*{Mechanics}
\begin{enumerate}
 
    \item \question{Write iterated integrals for $\iint_R 1 \ dA$ over the regions $R$ in both orders $dxdy$ and $dydx$.
\begin{enumerate}
	\item $R$ bounded by $y=e^{-x}$, $y=1$, and $x=\ln 3$.
	
	\item $R$ bounded by $y=x^2$ and $y=x+2$
    \end{enumerate}}{% answer goes here
    }
    {% solution goes here
    }
\item \question{Evaluate each of the following by sketching the region of integration and deciding on the best order of integration. Why did you choose the order that you did? 
	\begin{enumerate}
	    \item \[
	        \int_0^{\sqrt{\pi}} \int_y ^{\sqrt{\pi}} \cos(x^2) \ dx \ dy
	    \]
        \item \[
           \int_0^\pi \int_0^x x \sin (y)\ dy\ dx 
        \]
        \item 
        \[
            \iint_R xy^2\ dA
        \]
        where $R$ is the region bounded by $x=0$ and $x=\sqrt{1-y^2}$
	\end{enumerate}}{% answer goes here
    }
    {% solution goes here
    }
\end{enumerate}

\subsection*{Applications}
\begin{enumerate}[resume]
    \item \question{Find the mass of a triangular plate with vertices $(0, 0), (4, 0)$ and $(0, 1)$, given that its density at any point is $\rho(x,y)= x^2+y^2$}{% answer goes here
    }
    {% solution goes here
    }
\end{enumerate}
\subsection*{Extensions}
\begin{enumerate}[resume]
	\item \question{Find the volume of the solid bounded by the cylinder $y^2+z^2=4$ and the planes $x=2y$, $x=0$, $z=0$ in the first octant.}{% answer goes here
    }
    {% solution goes here
    }
\end{enumerate}
{}

\iftoggle{answers}{
\begin{center}{\large \textbf{Math 2551 Worksheet Answers: Double Integrals on General Regions}}
\end{center}

\begin{enumerate}
	
	\item $2+\frac{1}{2}\pi^2$
	
	\item \begin{enumerate}
		\item Negative
		\item Positive
		\item Zero
		\item Zero
		\item Zero
	\end{enumerate}
	
	
	\item \begin{enumerate}
		\item $\int_0^{\ln(3)} \int_{e^{-x}}^1\ dy\ dx$ and $\int_{1/3}^1 \int_{-\ln(y)}^{\ln(3)}\ dx\ dy$
		
		\item $\int_{-1}^2 \int_{x^2}^{x+2} \ dy\ dx$ and $\int_0^1 \int_{-\sqrt{y}}^{\sqrt{y}} \ dx\ dy + \int_1^4 \int_{y-2}^{\sqrt{y}}\ dx\ dy$
	\end{enumerate}
	\item $ \int_0^{\sqrt{\pi}} \int_0^{x} \cos(x^2) \ dy \ dx=0$
	\item $\dfrac{2}{15}$
	
	
	\item $16/3$
	
	\item $32/3$	
\end{enumerate}
}{}
\iftoggle{solutions}
{
Solutions go here in the same format.
}{}
