\fancyhead[C]{Section 12.4}
\fancyhead[R]{\daytwo}

\section*{\centering Chapter 12.4: Vector Products}

\subsection*{Mechanics}
\begin{enumerate}
   \item\question{ Let $P=(1,-1,2)$, $Q=(2,0,-1)$, and $R=(0,2,1)$. 
	\begin{enumerate}
		\item Find the area of the triangle determined by the points $P,Q$, and $R$.
		
		\item Find a unit vector normal to the plane containing $P$, $Q$, and $R$.
	\end{enumerate}
    }
    {% answer goes here

    }
    {% solution goes here
    } 
    \item \question{Find the volume of the parallelepiped spanned by the vectors $(1,2,3), (3,4,5), (-2,-1,0)$.}
    {% answer goes here
    }
    {% solution goes here
    }
    \item \question{Let $\bv = (v_1,v_2,v_3)$ be any nonzero vector. What are all of the vectors $\bf w$ for which $\bv \times {\bf w} = (0,0,0)$? }
    {% answer goes here
    }
    {% solution goes here
    }
    \item \question{Let  $\bf{u}$, ${\bf v}$, and $\bf{w}$ be vectors in $\mathbb{R}^3$. If the statement is \textit{always} true, answer true.  If the statement is \textit{ever} false, answer false.  Justify your answer.
	\begin{enumerate}
		\item $\bf{u} \cdot \bf{v} = \bf{v} \cdot \bf{u}$
		\item $\bf{u}\cdot \bf{u} = |\bf{u}|^2$
		\item $(\bf{u} \times \bf{u}) \cdot \bf{u}=0$
		
	\end{enumerate} }
    {% answer goes here
    }
    {% solution goes here
    }
	
	\item \question{Suppose ${\bf u}$, ${\bf v}$, and ${\bf w}$ are vectors in $\R^3$.  Which of the following make sense, and which do not?
	For those that make sense, is the result a vector or a scalar?
	\begin{enumerate}
		\item $({\bf u} \times {\bf v}) \cdot {\bf w}$ 
		\item ${\bf u} \times ({\bf v} \cdot {\bf w})$
		\item ${\bf u} \times ({\bf v} \times {\bf w})$ 
		\item ${\bf u} \cdot ({\bf v} \cdot {\bf w})$
	\end{enumerate}}
    {% answer goes here
    }
    {% solution goes here
    }
\end{enumerate}
\subsection*{Applications}
\begin{enumerate}[resume]
    \item In graphics rendering and CGI, vector products govern the way that light behaves. For example, the \textit{law of reflection} demands that a light ray reflecting off of a flat surface must reflect outwards with the same angle that it came in with. Suppose then, that a light source located at $(1,2,3)$ points towards the origin. What is the angle of reflection?
\end{enumerate}
\subsection*{Extensions}
\begin{enumerate}[resume]
\item \question{Let ${\bf u} = \langle 2, 3 \rangle$.  Find the maximum possible value for ${\bf u} \cdot {\bf v}$ if ${\bf v}$ is a unit vector,
and find a ${\bf v}$ which gives this maximum.  Then repeat the problem with ``maximum" replaced by ``minimum."}
    {% answer goes here
    }
    {% solution goes here
    }
    \item \question{Let $\bv= (1,1,1)$. Describe the set of all vectors $\bf{u},\bf{w}$ for which $\bf{u}\times\bf{w}$ is a scalar multiple of $\bv$. Can you interpret your answer pictorially? How would your answer change if $\bv$ was an arbitrary nonzero vector?}
    {% answer goes here
    }
    {% solution goes here
    }
\end{enumerate}
{}

\iftoggle{answers}{\begin{center}{\large \textbf{Math 2551 Worksheet 2 Answers: $\R^3$ and Cross Products}}
\end{center}


\begin{enumerate}
	
	
	\item Let $P=(1,-1,2)$, $Q=(2,0,-1)$, and $R=(0,2,1)$. 
	\begin{enumerate}
		\item $2\sqrt{6}$
		
		\item $\dfrac{1}{\sqrt{6}}\langle 2, 1, 1 \rangle$
	\end{enumerate}
	
	\item \begin{enumerate}
		\item True
		\item True 
		\item True
		
	\end{enumerate} 
	
	\item \begin{enumerate}
		\item Makes sense, scalar
		\item Does not make sense
		\item Makes sense, vector
		\item Does not make sense
	\end{enumerate}
	
	\item Max value is $\sqrt{13}$, given by $\bv=\bu/|\bu|$ and min value is $-\sqrt{13}$, given by $\bv=-\bu/|\bu|$.
\end{enumerate}
}{}
\iftoggle{solutions}
{
Solutions go here in the same format.
}{}
