\fancyhead[C]{Sections 14.3-14.8, 15.1-15.4}
	\fancyhead[R]{\dayseventeen}

\iftoggle{questions}{
\begin{center}{\large \textbf{Math 2551 Worksheet: Exam 2 Review}}
\end{center}


\begin{enumerate}
	
	
	\item Which of the following statements are true if $f(x, y)$ is differentiable
	at $(x_0 , y_0)$? Give reasons for your answers.
	\begin{enumerate}
		\item  If $\bu$ is a unit vector, the derivative of $f$ at $(x_0 , y_0)$ in the direction
		of $\bu$ is $(f_x(x_0 , y_0)\bi + f_y(x_0 , y_0)\bj) \cdot \bu$.
		\item The derivative of $f$ at $(x_0 , y_0)$ in the direction of $\bu$ is a vector.
		\item The directional derivative of $f$ at $(x_0 , y_0)$ has its greatest value
		in the direction of $\nabla f$.
		\item At $(x_0 , y_0)$, the vector $\nabla f$ is normal to the curve $f(x, y) = f(x_0 , y_0)$.
	\end{enumerate}
	
	\item Find $dw/dt$ at $t = 0$ if $w = \sin(xy + \pi), x = e^t,$ and $y =
	\ln(t + 1).$
	
	\item Find the extreme values of $f(x, y) = x^3 + y^2$ on the circle $x^2 + y^2 = 1$.
	
	\item Test the function $f(x,y)=x^3+y^3+3x^2-3y^2$ for local maxima and minima and saddle points and find the function's value at these points.
	
	\item Find the points on the surface $xy+yz+zx-x-z^2=0$ where the tangent plane is parallel to the $xy$-plane.
	
	\item Evaluate the integral $\displaystyle \int_0^1\int_{2y}^2 4\cos(x^2)\ dx\ dy$. Describe why you made any choices you did in the course of evaluating this integral.
	
	\item If $f(x,y)\geq 2$ for all $(x,y)$, is it possible that the average value of $f(x,y)$ on a unit disk centered at the origin is $\dfrac{2}{\pi}$?
	
	\item A swimming pool is circular with a 40 foot diameter.  The depth is constant along east-west lines and increases linearly from 2 feet at the south end to 7 feet at the north end.  Find the volume of water in the pool.
	
\end{enumerate}
}{}

\iftoggle{answers}{
\begin{center}{\large \textbf{Math 2551 Worksheet Answers: Exam 2 Review}}
\end{center}

\begin{enumerate}
	
	\item All are true except b).
	
	
	\item -1
	
	\item $\pm 1$
	
	\item Saddle at $(0,0)$ with $f(0,0)=0$, local min at $(0,2)$ of $-4$, local max at $(-2,0)$ of 4, saddle at $(-2,2)$ with $f(-2,2)=0$
	
	\item $(-1/2, 1/2, 1/2)$ and $(0,1,0)$
		
	\item $\sin(4)$
	
	\item No, this is less than $f(x,y)$ at all points, so it cannot possibly be the average value.
	
	\item $1800\pi$ cubic feet
\end{enumerate}
}{}
\iftoggle{solutions}
{
Solutions go here in the same format.
}{}
