\DocumentMetadata{
	lang        = en-US,
	pdfstandard = ua-2,
	pdfstandard = a-4f, %or a-4
	tagging=on,
	tagging-setup={math/setup={mathml-SE,mathml-AF}}%, math/alt/use=true} 
}
\documentclass[12pt]{article}
\usepackage{unicode-math}
\usepackage{amsmath}
\usepackage{theorem}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{etoolbox}
\usepackage{pgfplots}
%\usepackage{todonotes}
%\usepackage{tcolorbox}
%\usepackage{enumitem}
%\usepackage{verbatimbox}

\pgfplotsset{compat=1.18}
\topmargin-1cm \textheight 23cm \textwidth  17cm
\oddsidemargin-.1cm
\evensidemargin-.1cm
\parindent 0mm
\marginparwidth 2cm
\parskip 1.3ex plus 0.5ex minus 0.5ex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{header_def.tex}

\newtoggle{questions}
\newtoggle{solutions}
\newtoggle{answers}
\toggletrue{questions}   %print questions
%\toggletrue{answers}  %print answers
%\toggletrue{solutions} %print solutions

\newcommand{\question}[3]{\iftoggle{questions}{#1}{}

\iftoggle{answers}{\textbf{Answer:} #2}{}

\iftoggle{solutions}{\textbf{Solution:} #3}{}}

\begin{document}

% \begin{myverbbox}{\verbSection}
% \section{\centering stuff}
% \end{myverbbox}
% \begin{myverbbox}{\verbCurrent}
% \begin{center}
%      {\large \textbf{stuff}}
% \end{center}
% \end{myverbbox}
% \begin{myverbbox}{\verbQuestion}
% \question{question goes here}
%     {final answer goes here}
%     {solution goes here}
% \end{myverbbox}

% Things to work on:

% \todo[inline]{Add solutions to all worksheet days}
% \todo[inline]{Update problems to better ones as needed}

% \todo[inline]{Change all headers to be 

% \begin{minipage}{0.2\textwidth}
% \verbSection
% \end{minipage}

% instead of 

% \begin{minipage}{0.2\textwidth}
% \verbCurrent
% \end{minipage}
% }

% \todo[inline]{Add Learning Outcome information to the top of each worksheet as appropriate (starting w/ 12.5).  The Learning Outcomes are listed below the end document here.  Each worksheet should get at the top ``The Learning Outcomes associated with this worksheet are:'' followed by a list of all of the appropriate ones (usually just one or two).}

% \todo[inline]{Use new \begin{minipage}{0.2\textwidth}
%     \verbQuestion
% \end{minipage}

% format instead of the large blocks}

%\include{WS_12_1.tex}
% \include{WS_12_1.tex}
% \include{WS_12_4.tex}
% \include{WS_12_5.tex}
% \include{WS_12_6.tex}
% \include{WS_13_1.tex}
% \include{WS_13_2.tex}
% \include{WS_13_3.tex}
% \include{WS_13_4.tex}
% \include{WS_14_1.tex}
% \include{WS_14_2.tex}
% \include{WS_exam_1_review.tex}
% \include{WS_14_3.tex}
% \include{WS_14_4.tex}
 \include{WS_14_5.tex}
% \include{WS_14_6.tex}
% \include{WS_14_7_a.tex}
% \include{WS_14_7_b.tex}
% \include{WS_14_8.tex}
% \include{WS_15_1.tex}
% \include{WS_15_2.tex}
% \include{WS_15_3.tex}
% \include{WS_15_4.tex}
% \include{WS_exam_2_review.tex}
% \include{WS_15_5.tex}
% \include{WS_15_6.tex}
% \include{WS_15_7.tex}
% \include{WS_15_8.tex}
% \include{WS_16_1.tex}
% \include{WS_16_2.tex}
% \include{WS_16_3.tex}
% \include{WS_16_4.tex}
% \include{WS_16_5.tex}
% \include{WS_16_6.tex}
% \include{WS_16_7.tex}
% \include{WS_exam_3_review.tex}
%\include{WS_exam_final_review.tex}

%\include{HP_review_exam2.tex}
%\include{HP_review_exam3.tex}


\end{document}

\item \textbf{G1: Lines and Planes.} I can describe lines using the vector equation of a line. I can describe planes using the general equation of a plane. I can find the equations of planes using a point and a normal vector. I can find the intersections of lines and planes.  I can describe the relationships of lines and planes to each other. I can solve problems with lines and planes.
		
		\item \textbf{G2: Calculus of Curves.} I can compute tangent vectors to parametric curves and their velocity, speed, and acceleration. I can find equations of tangent lines to parametric curves. I can solve initial value problems for motion on parametric curves.
		
		\item \textbf{G3: Geometry of Curves.} I can compute the arc length of a curve in two or three dimensions and apply arc length to solve problems. I can compute normal vectors and curvature for curves in two and three dimensions.  I can interpret these objects geometrically and in applications.
		
		\item \textbf{G4: Surfaces.} I can identify standard quadric surfaces including: spheres, ellipsoids, elliptic paraboloids, hyperboloids, cones, and hyperbolic paraboloids. I can match graphs of functions of two variables to their equations and contour plots and determine their domains and ranges.

		\item \textbf{G5: Parameterization.} I can find parametric equations for common curves, such as line segments, graphs of functions of one variable, circles, and ellipses.  I can match given parametric equations to Cartesian equations and graphs. I can parameterize common surfaces, such as planes, quadric surfaces, and functions of two variables.

        \item \textbf{D1: Limits of Functions.} I can calculate the limits of some functions of two variables or and apply the Two-Path Test to determine if they do not exist. I can state the definition of continuity for functions of multiple variables.
        
		\item \textbf{D2: Computing Derivatives.} I can compute partial derivatives, total derivatives, directional derivatives, and gradients. I can use the Chain Rule for multivariable functions to compute derivatives of composite functions.
		
		\item \textbf{D3: Tangent Planes and Linear Approximations.} I can find equations for tangent planes to surfaces and linear approximations of functions at a given point and apply these to solve problems.
		
		\item \textbf{D4: Optimization.} I can locate and classify critical points of functions of two variables. I can find absolute maxima and minima on closed bounded sets. I can use the method of Lagrange multipliers to maximize and minimize functions of two or three variables subject to constraints. I can interpret the results of my calculations to solve problems.
		
		\item \textbf{I1: Double \& Triple Integrals.} I can set up double and triple integrals as iterated integrals over any region. I can sketch regions based on a given iterated integral.  
		
		\item \textbf{I2: Iterated Integrals.} I can compute iterated integrals of two and three variable functions, including applying Fubini's Theorem to change the order of integration of an iterated integral.
		
		\item \textbf{I3: Change of Variables.} I can use polar, cylindrical, and spherical coordinates to transform double and triple integrals and can sketch regions based on given polar, cylindrical, and spherical iterated integrals. I can use general change of variables to transform double and triple integrals for easier calculation.  I can choose the most appropriate coordinate system to evaluate a specific integral.
		
		\item \textbf{A1: Interpreting Derivatives.} I can interpret the meaning of a partial derivative, a gradient, or a directional derivative of a function at a given point in a specified direction, including in the context of a graph or a contour plot.
		
		\item \textbf{A2: Integral Applications.}  I can use multiple integrals to solve physical problems, such as finding area, average value, volume, or the mass or center of mass of a lamina or solid. I can interpret mass, center of mass, work, flow, circulation, flux, and surface area in terms of line and/or surface integrals, as appropriate.
		
		\item \textbf{V1: Line Integrals.} I can set up and evaluate scalar and vector field line integrals in two and three dimensions.
					
		\item \textbf{V2: Conservative Vector Fields.} I can test for conservative vector fields and find potential functions. I can state and apply the Fundamental Theorem of Line Integrals.
					
		\item \textbf{V3: Generalizations of the FTC.} I can state and apply Green's Theorem, Stokes' Theorem and the Divergence Theorem to solve problems in two and three dimensions. I can choose which theorem is appropriate for different integrals. I can compute curl and divergence of vector fields.
					
		\item \textbf{V4: Surface Integrals.} I can set up and compute surface integrals for scalar and vector valued functions.